I've Got Nothing to Hide: \\ Exploring Privacy in Art, Fiction, and Film

### 2013-09-27 nothing_to_hide/presentation.tex
Reviewer's comments.

\begin{frame}
\frametitle{A Tale of Two Dystopias}
\begin{itemize}
\item Orwellian
  \begin{itemize}
  \item Surveillance state.
  \item Social control through over presence.
  \end{itemize}
\item Kafkaesque
  \begin{itemize}
  \item Information processing affects the power relationship.
  \item Frustrate individuals and creates helplessness and powerlessness.
  \end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{The problem with the argument}

@@

The issue, however, often is not whether the NSA or other government
agencies should be allowed to engage in particular forms of information
gathering; rather, it is what kinds of oversight and accountability we
want in place when the government engages in searches and seizures.

@@

\begin{frame}
\frametitle{\emph{V for Vendetta} 2005}

@@

\begin{itemize}
\item Would you keep your blinds open in NYC if you lived there?  What
  if your neighbor was taking pictures?
\item When, if ever, would you consider filling a Freedom of
  Information Act (FOIA) request for your file?
\item The TSA back-scatter machines have raised privacy concerns
  because of the revealing images.  Would you / did you go throw them?
  Did you feel any pressure to choose the scanner over the pat-down?

>>>>

\begin{frame}
\frametitle{A Tale of Two Dystopias}
\begin{itemize}
\item Orwellian
  \begin{itemize}
  \item Surveillance state.
  \item Social control through overt presence.
  \end{itemize}
\item Kafkaesque
  \begin{itemize}
  \item Information processing affects the power relationship.
  \item Frustrate individuals and creates helplessness and powerlessness.
  \end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{The problem with ``I have nothing to hide''}

@@

``The issue, however, often is not whether the NSA or other government
agencies should be allowed to engage in particular forms of information
gathering; rather, it is what kinds of oversight and accountability we
want in place when the government engages in searches and seizures.''

@@

\begin{frame}
\frametitle{\emph{V for Vendetta} (2005)}

@@

\begin{itemize}
\item Would you keep your blinds open in NYC if you lived there?  What
  if your neighbor was taking pictures?
\item When, if ever, would you consider filing a Freedom of
  Information Act (FOIA) request for your file?
\item The TSA back-scatter machines have raised privacy concerns
  because of the revealing images.  Would you / did you go throw them?
  Did you feel any pressure to choose the scanner over the pat-down?
